<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{a}
-->

# Introduction 

`choroplethrCaCensusTract` facilitates the rendering of [choropleth maps](http://en.wikipedia.org/wiki/Choropleth_map) of [US Census Tracts](https://www.census.gov/geo/reference/gtc/gtc_ct.html) in the state of California.

```{r warning=FALSE}
library(choroplethrCaCensusTract)

data(df_pop_ca_tract)

?df_pop_ca_tract
?ca_tract_choropleth

ca_tract_choropleth(df_pop_ca_tract,
                    title  = "2012 Population Estimates\n California Census Tracts",
                    legend = "Population")
```

Census Tracts normally have between 1,800 and 8,000 people. Therefore, on a state map, it is not possible to distinguish the tracts in urban areas. We can zoom in on individual counties by using the `county_zoom` parameter. `county_zoom` takes a vector of [County FIPS Codes](http://en.wikipedia.org/wiki/FIPS_county_code).

```{r warning=FALSE}
# 6075 is the FIPS code for San Francisco County
ca_tract_choropleth(df_pop_ca_tract,
                    title       = "2012 Population Estimates\n San Francisco Census Tracts",
                    legend      = "Population",
                    county_zoom = 6075)
```

# 2013 Summary Census Data

`choroplethrCaCensusTract` ships with a data.frame, `?df_ca_tract_demographics`, that has eight demographic variables from the 2013 5-year American Community Survey (ACS).

```{r warning=FALSE}
data(df_ca_tract_demographics)
?df_ca_tract_demographics
colnames(df_ca_tract_demographics)

df_ca_tract_demographics$value = df_ca_tract_demographics$per_capita_income
ca_tract_choropleth(df_ca_tract_demographics,
                    title       = "2013 San Francisco Census Tracts\n Per Capita Income",
                    legend      = "Dollars",
                    num_colors  = 1,
                    county_zoom = 6075)
```

# Other Census Data

You can get the values of the eight variables from `df_ca_tract_demographics` from other surveys as well. See `?get_ca_tract_demographics`. 

You can also map data from any table from the ACS that is available thru their API and provides data at the level of California Census Tracts. See `?ca_tract_choropleth_acs`. 